Earth at night*\\ {\footnotesize \textsuperscript{*}The visualisation of average radiance in specific area}

### 2021-09-12 paper/main.tex
update format

    Low Earth Orbit (LEO) is an orbit relatively close to the surface of the earth. It is usually located at an altitude of fewer than 
    2000 kilometers, but it may be as low as 400 kilometers above the earth. Compared to other orbits, it is low, but still far from the 
    surface of the earth \cite{earthdata28:online}.It is the most commonly used orbit for satellite imaging because it is possible to take 
    higher resolution images close to the surface. It is also the orbit used by the International Space Station (ISS) because it is easier 
    for astronauts to travel to and from it at shorter distances. The satellite in this orbit travels at a speed of about 7.8 kilometers per 
    second; at this speed, it takes about 90 minutes for the satellite to orbit the earth, which means that the International Space Station 
    orbits the earth about 16 times a day \cite{ESAkerne12:online}.

@@

    The orbit of a geostationary satellite can only be achieved at an altitude very close to 35,786 kilometers, and the satellite can 
    be fixed at one longitude of the equator. There are hundreds of communication satellites and several weather satellites in such orbits.

@@

    Very Low Frequency (VLF): ELF is extremely low frequency and extremely low frequency, and its frequency is in the range of 
    300 Hz to 30 kHz. It is a kind of radio wave, just like AM/FM signal, but with a lower frequency. It is very useful because 
    it is mainly reflected at a height of 60-90 kilometers in the D zone of the earth's ionosphere, so it is effectively guided 
    to a global distance in the earth's ionospheric waveguide. It is widely used to set up radio receivers almost anywhere on 
    the earth \cite{Introduc19:online}. This signal can receive short radiation from lightning strikes in half of the earth.

@@

The main architecture is shown as Fig.~\ref{fig2}. First of all, two kinds of IaC platform, which are Ansible and CloudFormation.
Ansible is the first choice that can be esily used in most of situations. When some service need to configure complicatedly, CloudFormation is 
better. Secondly, NAT and ELB are the only entrance to the project. That is the best practice for network security that can mitigate the effects 
of public cyberattacks. Thirdly, IAM roles are used at all kinds of important scenarios, for example, deployment, database visiting, various services visiting.

@@

The second step is the sbunet design, which is shown as Fig.~\ref{subnet}. There are there different subnets using for services in different layers. And also, 
these subnet configurations help the step one to isolate the public network environment. The subnets named Intranet2 and Intranet3 are the isolated frontend 
instances. The benefit of this design is isolate the same functions into different partitions. When a part of entire demo are hacked, it is easy 
to close this part to avoid more damage. The third subnet is the core subnet which is connected with database.

>>>>

    Low Earth Orbit (LEO) is an orbit relatively close to the surface of the earth (Fig.~\ref{LEO}) . It is usually located at an altitude of fewer than 
    2000 kilometers, but it may be as low as 400 kilometers above the earth. Compared to other orbits, it is low, but still far from the 
    surface of the earth \cite{earthdata28:online}.It is the most commonly used orbit for satellite imaging because it is possible to take 
    higher resolution images close to the surface. It is also the orbit used by the International Space Station (ISS) because it is easier 
    for astronauts to travel to and from it at shorter distances. The satellite in this orbit travels at a speed of about 7.8 kilometers per 
    second; at this speed, it takes about 90 minutes for the satellite to orbit the earth, which means that the International Space Station 
    orbits the earth about 16 times a day \cite{ESAkerne12:online}.

@@

    The orbit of a geostationary satellite can only be achieved at an altitude very close to 35,786 kilometers, and the satellite can 
    be fixed at one longitude of the equator (Fig.~\ref{Geostationary}). There are hundreds of communication satellites and several weather satellites in such orbits.

@@

    Very Low Frequency (VLF): ELF is extremely low frequency and extremely low frequency, and its frequency is in the range of 
    300 Hz to 30 kHz (Fig.~\ref{Spectrum}). It is a kind of radio wave, just like AM/FM signal, but with a lower frequency. It is very useful because 
    it is mainly reflected at a height of 60-90 kilometers in the D zone of the earth's ionosphere, so it is effectively guided 
    to a global distance in the earth's ionospheric waveguide. It is widely used to set up radio receivers almost anywhere on 
    the earth \cite{Introduc19:online}. This signal can receive short radiation from lightning strikes in half of the earth.

@@

The main architecture is shown as Fig.~\ref{fig2}. First of all, two kinds of IaC platform, which are Ansible and CloudFormation, are used for deployment.
Ansible is the first choice that can be esily used in most of situations. When some service need to configure complicatedly, CloudFormation is 
better. Secondly, NAT and ELB are the only entrance to the project. That is the best practice for network security that can mitigate the effects 
of public cyberattacks. Thirdly, IAM roles are used at all kinds of important scenarios, for example, deployment, database visiting, various services visiting.

@@

The second step is the subnet design, which is shown as Fig.~\ref{subnet}. There are there different subnets using for services in different layers. And also, 
these subnet configurations help the step one to isolate the public network environment. The subnets named Intranet2 and Intranet3 are the isolated frontend 
instances. The benefit of this design is isolate the same functions into different partitions. When a part of entire demo are hacked, it is easy 
to close this part to avoid more damage. The third subnet is the core subnet which is connected with database.
